Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-18 appendix.tex
typo

In the manuscript, the training cost of adversarial training is caluclated as
$\eta+1$, which is the number of forward-backward propagation involved in each
iteration of the training process, in order to reflect the training efficiency
(gain as high robustness as possible given a fixed number of foward-backward
calculation for adversarial training) of different defense methods.
%
Specifically, PGD creates adversarial examples from the $\eta$ times of
forward-backward computation.
%
With the resulting adversarial examples, the network requires once
more forward-backward computation to update the model parameters.

>>>>

In the manuscript, the training cost of adversarial training is caluclated as
$\eta+1$, which is the number of forward-backward propagation involved in each
iteration of the training process, in order to reflect the training efficiency
(gain as high robustness as possible given a fixed number of forward-backward
calculation for adversarial training) of different defense methods.
%
Specifically, PGD creates adversarial examples from the $\eta$ times of
forward-backward computation.
%
With the resulting adversarial examples, the network requires once
more forward-backward computation to update the model parameters.
